\documentclass[11pt]{article}
\usepackage{times}
\usepackage[margin=1in]{geometry}

\begin{document}

\noindent
Dear IJCAI 2026 Program Chairs and Reviewers,

\vspace{1em}

We respectfully submit our manuscript entitled
\emph{``SASS: Structure-Aware Surrogates for Learning to Schedule''}
for consideration at IJCAI~2026.

\vspace{0.5em}

This submission is a revised and extended version of a paper previously submitted to
ECAI~2025.
In accordance with IJCAI resubmission policies, we provide the following additional materials:

\begin{enumerate}
    \item We attach the full ECAI~2025 decision letter, metareview, and all reviewer reports
    \emph{verbatim}, with no modifications to the content.
    Author names have been removed everywhere solely to preserve anonymity.
    
    \item We attach the version of the paper as submitted to ECAI~2025, for reference.
    
    \item The current IJCAI~2026 submission substantially improves upon the ECAI~2025 version.
    In particular, the new manuscript:
    \begin{itemize}
        \item Generalizes the original surrogate-loss idea into a unified
        \emph{structure-aware surrogate scheduling (SASS)} framework applicable to a broader
        class of surrogate-friendly scheduling problems.
        \item Extends the methodology beyond single-machine SCT minimization to include
        two-machine flow shop scheduling with makespan minimization via Johnson’s rule.
        \item Provides clearer formalization, stronger theoretical justification, and a more
        detailed connection between critical decisions, objective impact, and surrogate design.
        \item Expands the empirical evaluation, including additional synthetic experiments,
        runtime analysis, and a strengthened real-world outpatient scheduling case study.
    \end{itemize}
\end{enumerate}

\vspace{0.5em}

We believe these changes address the key concerns raised in the prior reviews, in
particular regarding scope, generality, and the support for the core surrogate-based
contribution.

\vspace{1em}

Thank you for your time and consideration.

\vspace{1em}

\noindent
Sincerely,\\
The Authors

\end{document}
